MP MetaAnalysis

### 2018-10-23 Paper_Analyses.Rmd
convert to papaja, temporary references fix

---
title: "MP MetaAnalysis"
author: "Christina Bergmann and Katie Von Holzen"
date: '`r format(Sys.Date(), "%d %B, %Y")`'
output: 
  pdf_document:
    toc: true

bibliography: references.bib
---
```{r Setup, echo = FALSE, warning=FALSE, warning = FALSE, error = FALSE, message = FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, tidy = TRUE, message = FALSE, error = FALSE)

### Load libraries

library(metafor)
library(meta)
library(pwr)
library(knitr)
library(ggplot2)
library(wesanderson)
library(grid)
library(gridExtra)
library(xtable)
library(schoRsch)
library(multcomp)
library(poibin)
library(tidyverse)

# set Table count at 0
t_num <- 0

# set Figure count at 0
f_num <- 0

@@

#[CHRISTINA: I prefer exact p-values with more granularity]

@@

# [CHRISTINA This should not be necessary]
#cur_dir <- getwd()

@@

@@

[KATIE] THIS TABLE IS DEFINITELY NOT FINISHED!
[CHRISTINA suggestions: N features should be a range and exclude 0; we could abbreviate Comperehension/Production to Comp./Prod., etcetc]

@@

t_num <- t_num+1

@@

# Not sure about this plot
#pi <- dat[,c("short_cite", "publication_status")]
#pi <- unique(pi)

#c.plot <- ggplot(pi, aes(x= publication_status)) + 
#  geom_text(stat='count', aes(label=..count..), vjust=-1, size = 5)+
#  geom_bar(stat="count")+
#  coord_cartesian(ylim = c(0, 30))+
#  apatheme+
#  theme(axis.text.x = element_text(size = 20, angle = -45, hjust = .11),
#        axis.title.x = element_blank())

#c.plot

#  jpeg(filename = "figures/Pub_count.jpg", 
#       width = 500, height = 500, units = "px")

#  c.plot

#  dev.off()

@@

kable(es_info)
#table(dat$es_method, dat$short_cite)
# only missing from:
# Bailey & Plunkett (2002) <- crazy old data
# Renner (2017) <- just finished phd
# Tamasi (2016) <- standard deviations are wrong
#table(db_ET_MP$es_method)

#[KATIE] Can you also rename the factors here (like t_one)?
#[CHRISTINA] Mpt sire what you man, like in the table? You rename things later on, so why not. 
```

@@

We calculated Hedges' *g* using the raw means and standard deviations reported in the paper (*n* = `r with(dat, n_distinct(short_cite[es_method == "group_means_one" | es_method == "group_means_two"]))`) or using reported t-values (*n* = `r with(dat, n_distinct(short_cite[es_method == "t_one" | es_method == "t_two"]))`). Raw means and standard deviations were extracted from figures for `r with(dat, n_distinct(short_cite[ x_from_graph == "yes"]))` papers. In a within-participation design, when two means are compared (i.e. looking during pre- and post-naming) it is necessary to obtain correlations between the two measurements at the participant level to calculate effect sizes and effect size variance based on t-values. One paper reported this correlation [CHRISTINA: Can we cite this??]; we were able to compute correlations using means, standard deviations, and t-values [CHRISTINA: can we add N?] (following Csibra, et al. 2016, Appendix B; see also Rabagliati, Ferguson, & Lew-Williams, 2018). Correlations were imputed for the remaining papers (see Black & Bergmann, 2017, for the same procedure). We could compute a total of `r sum(dat$is_mp == 0)` effect sizes for correct pronunciations and `r sum(dat$is_mp == 1)` for mispronunciations.

@@

[CHRISTINA: Do you think we have to revise this section? I think it's the same as in the proceedings paper.]

@@

[CHRISTINA: Let's both reread the full paper once it is ready and check that this is properly motivated and whether we do need to list them all. For now I think the last sentence is fine, but I would tend to prefer a reminder for the forgetful reader.]

@@

[CHRISTINA: If we want to interpret here, how about the next bit.]

The stronger publication bias for correct pronunciation might reflect the status of this condiction as a control. If infants were not looking to the target picture after hearing the correct label, the overall experiment design is called into questions. However, due to the small effect and sample sizes (which we will discuss in the following sections in more detail) one would expect the regular occurrence of null results even though as population infants would reliably show the expected object identification effect.

@@

[CHRISTINA: CAn you add the stats for the non-sig results?]

Taken together, these results suggest a tendency in the literature towards publication bias. As a result, our meta-analysis may systematically overestimate effect sizes and we therefore interpret all estimates with caution. Yet, the p-curve analysis suggests that overall, the literature contains evidential value, reflecting a "real" effect. We therefore continue our meta-analysis.

@@

We first calculated the meta-analytic effect for object identification, i.e. looks to the target image in response to correctly pronounced words. The variance-weighted meta-analytic effect size Hedges' *g* was `r r2(sum_eff$estimate)` (SE = `r r2(sum_eff$se)`) which was significantly different from zero (95% CI [`r r2(sum_eff$ci.lb)`, `r r2(sum_eff$ci.ub)`], *p* `r psig(sum_eff$pval)`). This is a rather large effect size (according to the criteria set by Cohen, 1988; see also Bergmann, et al., 2018; for comparative meta-analytic effect sizes in language acquisition research). That the effect size is significantly above zero suggests that when presented with the correctly pronounced label, infants fixated the corresponding object. Our analysis of funnel plot asymmetry, however, found evidence for publication bias, which might lead to an overestimated effect sizes as smaller, non-significant results might not be published. Although the effect size Hedges' *g* may be overestimated for object identification in response to correctly pronounced words, the p-curve results and a CI lower bound of `r r2(sum_eff$ci.lb)` suggests that this result is robust even when correcting for publication bias.

[CHRISTINA: Can you explain what the CI lower bound means here? I don't follow.]

@@

[CHRISTINA] CAN YOU ADD ESTIMATES AND THEIR CIS?? Ideally everywhere where you report a p-value

@@

[KATIE] I DON'T KNOW HOW TO INTERPRET THESE RESULTS... THE FIXED EFFECTS MODEL ISN'T SIGNIFICANT FOR ANY OF THESE. IS THAT MEANINGFUL?
[CHRISTINA] SO WE DON'T WANT TO INTERPRET THE FIXED EFFECTS MODEL AT ALL, IT IS NOT SUITABLE BECAUSE THERE IS VARIANCE BETWEEN EVERY RECORD (LANGUAGE ETC).
I WOULD INTERPRET THE OVERALL CORRELATION AND THE CI, NOT THE P-VALUE (IN GENERAL). I ALSO WONDER WHETHER WE SHOULD MOVE THE SUBSET ANALYSES TO THE SUPPLEMENTARY MATERIALS AND JUST SAY OVERALL WE SEE NO RELATIONSHIPS AND CORRELATION COEFFICIENTS CONSISTENYL BELOW .1
WE THEREFORE MUST CONCLUDE THAT WITHIN NARROW AGE GROUPS VOCABULARY DOES NOT INFLUENCE ANYTHING WE LOOK AT. WE CANNOT DO THIS ANALYSIS FPOR MP SENSITIVITY BECAUSE WE DON'T HAVE THE NECESSARY RAW DATA.
(BUT I WONDER WHETHER WE COULD ENCODE THE REPORTED INTERACTION TERMS AND THE CORRELATION AND THEN DO SOMETHING WITH THAT?)

@@

### Size of mispronunciation

[CHRISTINA] I PREFER NUMBER OF FEATURES TO SIZE SOMEHOW

@@

[KATIE] DOES THE ABOVE PARAGRAPH NEED MORE MOTIVATION? SHOULD IT EVEN BE INCLUDED?
[CHRISTINA] I THINK IT\S GREAT!

@@

@@

# References

>>>>

---
title             : "The development of infants' responses to mispronunciations - A Meta-Analysis"
shorttitle        : "Mispronunciation Meta-Analysis"

author: 
  - name          : "Katie Von Holzen"
    affiliation   : "1,2"
    corresponding : yes    # Define only one corresponding author
    address       : "0221A LeFrak Hall, University of Maryland, College Park, MD 20742"
    email         : "katie.m.vonholzen@gmail.com"
  - name          : "Christina Bergmann"
    affiliation   : "3,4"

affiliation:
  - id            : "1"
    institution   : "Language Development Laboratory, University of Maryland, USA"
  - id            : "2"
    institution   : "Laboratoire Psychologie de la Perception, Université Paris Descartes"
  - id            : "3"
    institution   : "Max Planck Institute for Psycholinguistics, Nijmegen, the Netherlands"
  - id            : "4"
    institution   : "LSCP, Departement d'Etudes Cognitives, ENS, EHESS, CNRS, PSL Research University"

abstract: |
  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.

  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.

  One sentence clearly stating the **general problem** being addressed by  this particular study.

  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).

  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.

  One or two sentences to put the results into a more **general context**.

  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.

keywords          : "keywords"
wordcount         : "X"

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no
citeproc          : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

```{r Setup, echo = FALSE, warning=FALSE, warning = FALSE, error = FALSE, message = FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, tidy = TRUE, message = FALSE, error = FALSE)

# bibliography      : ["MISP_MA_BIB.bib"]

# [KATIE] BIBLIOGRAPHY CURRENTLY REMOVED, AS IT IS CAUSING ERRORS WITH PAPAJA
# THIS IS PARTIALLY DUE TO THE WAY I CREATE IT USING MENDELEY. 
# TOO LAZY FOR THE MOMENT TO COMPLETELY OVERHAUL THIS

# BUT, OTHER PROBLEMS INCLUDE HAVING PAPAJA INSTALLED IN THE USER AND NOT SYSTEM LIBRARY
# https://github.com/crsh/papaja/issues/162
# devtools::with_libpaths(new = "/usr/lib/R/library/", install_github('crsh/papaja'))

# AND THE NEED TO SET citeproc: no
# https://github.com/crsh/papaja/issues/96

# STILL NEED TO FIGURE OUT WHAT ACTUAL PROBLEM IS, THIS IS CURRENTLY JUST A WORKAROUND

### Load libraries
library(papaja)
library(metafor)
library(meta)
library(pwr)
library(knitr)
library(ggplot2)
library(wesanderson)
library(grid)
library(gridExtra)
library(xtable)
library(schoRsch)
library(multcomp)
library(poibin)
library(tidyverse)

@@

@@

@@

# Introduction

Acquiring a first language means that young learners are solving a host of tasks in a short amount of time. As infants develop into toddlers during their second and third years they learn new words in earnest while simultaneously refining their knowledge about the sounds that make up these words. Before children can correctly pronounce a word, they already show evidence of sensitivity to slight variations in the phonological form of that word. This mispronunciation sensitivity reflects the specificity with which infants represent the phonological information of familiar words and are sensitive to changes that might signal a change in word meaning. As infants continue to develop into expert language users, their language processing matures and becomes more efficient. In a mature phono-lexical system, word recognition must balance flexibility to slight variation (e.g., speaker identity, accented speech) while distinguishing between phonetic details that differentiate words in their native language (e.g. cat-hat). In this paper, we aggregate and analyze the almost 20 years of literature investigating mispronunciation sensitivity in infants in an attempt to uncover its characteristics and the trajectory of its development.

  At the turn of the millenia, infant language acquisition researchers had established that during their first years of life, infants are sensitive to changes in the phonetic detail of newly segmented words (Jusczyk & Aslin, 1995) and learned minimal pairs (Stager & Werker, 1997). Furthermore, when presented with familiar image pairs, children fixate on one image upon hearing its label (Fernald, Pinto, Swingley, Weinberg, & McRoberts, 1998). Swingley and Aslin (2000) were the first to tie these lines of research together and investigate mispronunciation sensitivity in infant familiar word recognition: Children aged 18 to 23 months learning American English were presented with pairs of images (e.g. baby, dog) and their eye movements to each image were coded offline. On "correct" trials, children heard the correct label for one of the images (e.g. baby). On "mispronounced" trials, children heard a mispronounced label of one of the images (e.g. vaby). Mean proportion of fixation to the target image (here: a baby) was calculated for both correct and mispronounced trials by dividing the target looking time by the sum of total looking time to both target and a distractor (proportion of target looking or PTL). Mean fixations in correct trials were significantly greater than in mispronounced trials, although looks to the target were significantly greater than chance in both types of trials. We refer to this pattern of a difference between looks to correct and mispronounced words as *mispronunciation sensitivity* and of looks to the target image above chance as *recognition*. Swingley and Aslin (2000) concluded that already before the second birthday, children represent words with sufficient detail to be sensitive to mispronunciations.

  The study of Swingley and Aslin (2000) as well as subsequent studies examining mispronunciation sensitivity address two complementary concepts in early phonological development: *phonological constancy* and *phonological distinctiveness*. Phonological constancy is the ability to accept phonological variation across different instances of a word, as long as the variation does not compromise the overall identity of the word. For example, different speakers - particularly across genders and accents - produce the same word with notable acoustic variation, although the word remains the same. In contrast, phonological distinctiveness describes the ability to differentiate between different words that happen to be phonologically similar, such as bad/bed or cat/hat. To successfully recognize words, infants must therefore simultaneously use both phonological constancy and distinctiveness to determine where phonological variation is appropriate and where it changes a word's meaning.

  In the current study, we focus on infants' developing ability to correctly apply the principles of phonological distinctiveness and constancy by using a meta-analytic approach to investigate mispronunciation sensitivity. Considering that infants are sensitive to mispronunciations and that, in general, their processing matures with development, we examine the shape of mispronunciation sensitivity over the course of the second and third year. There are three distinct possibilities how mispronunciation sensitivity might change as infants become native speakers, which are all respectively predicted by theoretical accounts and supported by single studies. By aggregating all publicly available evidence using meta-analysis, we can examine developmental trends making use of data from a much larger and diverse sample of infants. Before we outline the meta-analytical approach and its advantages in detail, we first discuss the proposals this study seeks to disentangle and the data supporting each of the accounts.

  Young infants may begin cautiously in their approach to word recognition, rejecting any phonological variation in familiar words and only later learning to accept appropriate variability. According to the Perceptual Attunement account, this describes a shift away from specific native phonetic patterns to a more mature understanding of the abstract phonological structure of words (Best 1994, 1995). This shift is predicted to coincide with the vocabulary spurt around 18 months, and is therefore related to vocabulary growth. In this case, we would expect the size of mispronunciation sensitivity to be larger at younger ages and *decrease* as the child matures and learn more words, although children continue to detect mispronunciations.
Indeed, young infants are less likely than older infants to demonstrate recognition of familiar words (Best, Tyler, Gooding, Orlando, & Quann, 2009; Mulak, Best, & Tyler, 2013) or learn new words (Schmale, Hollich, & Seidl, 2011) from accented speakers.

  According to a different theoretical framework, young infants may instead begin with phonologically broad representations for familiar words and only refine their representations as language experience accumulates. PRIMIR (Processing Rich Information from Multidimensional Interactive Representations; Curtin & Werker, 2007; Werker & Curtin, 2005; Curtin, Byers-Heinlein, & Werker, 2011) describes the development of phonemic categories emerging as the number of word form-meaning linkages increases. Vocabulary growth, therefore, promotes more detailed phonological representations in familiar words. Following this account, we predict an *increase* in mispronunciation sensitivity as infants mature and add more words to their growing lexicon.

  Finally, sensitivity to mispronunciation may not be modulated by development at all. Infants' overall language processing becomes more efficient, but their sensitivity to mispronunciations may not change. Across infancy and toddlerhood, mispronunciations would thus be detected and lead to less looks at a target than correct pronunciations, but the size of this effect would not change, nor be related to vocabulary size. This pattern is not predicted by any mainstream theory of language acquisition, but for completeness we mention it here.

  Research following the seminal study by Swingley and Aslin (2000) has extended mispronunciation sensitivity to infants as young as 12 months (Mani & Plunkett, 2010), indicating that from early stages of the developing lexicon onwards, infants can and do detect mispronunciations. Regarding the change in mispronunciation sensitivity over development, however, only a handful of studies have compared more than one age group on the same mispronunciation task (see Table X), making the current meta-analysis very informative. One study has found evidence for infants to become *less* sensitive to mispronunciations as children develop. Mani and Plunkett (2011) presented 18- and 24-month-olds with mispronunciations varying in the number of features changed (see below for a discussion of the role of features). 18-month-olds were sensitive to mispronunciations, regardless of the number of features changed. 24-month-olds, in contrast, fixated the target image equally for both correct and 1-feature mispronounced trials, although they were sensitive to larger mispronunciations. In other words, for 1-feature mispronunciations at least, sensitivity decreased from 18 to 24 months, providing support to the prediction that mispronunciation sensitivity may decrease with development.

  In contrast, other studies have found evidence for *greater* mispronunciation sensitivity as children develop. More precisely, the difference in target looking for correct and mispronounced trials is smaller in younger infants and grows as infants develop. Mani and Plunkett (2007) tested 15-, 18-, and 24-month-olds learning British English; although all three groups were sensitive to mispronunciations, 15-month-olds showed a less robust sensitivity. An increase in sensitivity to mispronunciations has also been found from 20 to 24 months (van der Feest & Fikkert, 2015) and 15 to 18 months (Altvater Mackensen et al., 2013) in Dutch infants, as well as German infants from 22 to 25 months (Altvater-Mackensen, 2010). Furthermore, van der Feest and Fikkert (2015) found that sensitivity to specific kinds of mispronunciations develop at different ages depending on language infants are learning. In other words, the native language constraints which *kinds* of mispronunciations infants are sensitive to first, and that as infants develop, they become sensitive to other mispronunciations. These studies award support to the prediction that mispronunciation sensitivity improves with development.

Finally, some studies have found no difference in mispronunciation sensitivity at different ages. Swingley and Aslin (2000) tested infants over a wide age range of 5 months (18 to 23 months).  They found that age correlated with target fixations for both correct and mispronounced labels, whereas the difference between the two (mispronunciation effect) did not. This suggests that as children develop, they are more likely to look at the target in the presence of a mispronounced label and that age is not related to mispronunciation sensitivity. A similar response pattern has been found for British English learning infants aged between 18 and 24 months (Bailey & Plunkett, 2002) as well as younger French-learning infants at 12 and 17 months (Zesiger, Lozeron, Levy, & Frauenfelder, 2012). These studies award support to the prediction that mispronunciation sensitivity does not change with development.

  Why would mispronunciation sensitivity change as infants develop, and would it increase or decrease? The main hypothesis is related to vocabulary growth. Both the Perceptual Attunement (Best, 1994; 1995) and PRIMIR (Curtin & Werker, 2007; Werker & Curtin, 2005; Curtin, Byers-Heinlein, & Werker, 2011) accounts situate a change in mispronunciation sensitivity occurring along with an increase in vocabulary size, particularly with the vocabulary spurt at about 18 months. Knowing more words helps infants shift their focus to the relevant phonetic dimensions needed for word recognition. On the one hand, a smaller lexicon does not require full specification to differentiate between words; as more phonologically similar words are learned, so does the need to have fully detailed representations for those words (Charles-Luce & Luce, 1995). On the other hand, a growing vocabulary is also related to more experience or familiarity with words, which may sharpen the detail of their representation (Barton, 1980).

  Yet, the majority of studies examining a potential association between mispronunciation sensitivity and vocabulary size have concluded that there is no relationship (Swingley & Aslin 2000; 2002; Bailey & Plunkett, 2002; Zesiger, Lozeron, Levy, & Frauenfelder, 2012; Swingley, 2009; Ballem & Plunkett, 2005; Mani & Plunkett, 2007; Mani, Coleman, & Plunkett, 2008). One notable exception comes from Mani and Plunkett (2010: keps and tups). Here, 12-month-old infants were divided into a low vocabulary and high vocabulary group based group median vocabulary size. High vocabulary infants showed greater sensitivity to vowel mispronunciations than low vocabulary infants, although this was not the case for consonant mispronunciations. Taken together, although receiving considerable support from theories of phono-lexical processing in language acquisition, there is very little evidence for a role of vocabulary size in mispronunciation sensitivity. In our current meta-analysis, we include the relationship between mispronunciation sensitivity and vocabulary size to further disentangle the disconnect between theory and experimental results.

  Next to this core theoretically relevant investigation of the shape of development of infants' mispronunciation sensitivity, we take the opportunity of a systematic aggregation of data to address open questions regarding differences in experiment design and whether changes in procedure and stimuli tap into significantly different aspects of infants' ability to detect mispronunciations.

  In designing their mispronunciation stimuli, Swingley and Aslin (2000) chose consonant mispronunciations that were likely to confuse adults (Miller & Nicely, 1955). Subsequent research has settled on systematically modulating phonemic features to achieve mispronunciations of familiar words. By utilizing mispronunciations consisting of phonemic changes, these experiments examine infants’ sensitivity to factors that change the identity of a word on a measurable level (i.e. 1-feature, 2-features, 3-features, etc.). The importance of controlling for the degree of phonological mismatch, as measured by number of features changed, is further highlighted by studies that find graded sensitivity to both consonant (White & Morgan, 2008) and vowel (Mani & Plunkett, 2011) feature changes.

  Although most research examining sensitivity to mispronunciations follows a similar design, there are some notable differences.  For example, Swingley and Aslin (2000) presented infants with pairs of familiar images, one serving as the labeled target and one as the unlabeled distractor. In contrast, White and Morgan (2008; see also Mani & Plunkett, 2011; Skoruppa et al., 2013; Swingley, 2016) presented infants with pairs of familiar (labeled target) and unfamiliar (unlabeled distractor) objects. By using an unfamiliar object as a distractor, the infant is presented with a viable option onto which the mispronounced label can be applied (Halberda, 2003; Markman, Wasow, & Hansen, 2003). Infants ages 24 and 30 months associate a novel label with an unfamiliar object, although only 30-month-olds retained this label-object pairing (Bion, Borovsky, and Fernald, 2013). In contrast, 18-month-olds did not learn to associate a novel label with an unfamiliar object, providing evidence that this ability is developing from 18 to 30 months. We may find that if mispronunciation sensitivity changes as children develop, that this change is modulated by whether the distractor used is familiar or unfamiliar. Although mispronunciation sensitivity in the presence of a familiar compared to unfamiliar distractor has not been directly compared, the baseline preference for familiar compared to novel stimuli is also thought to change as infants develop (Hunter & Ames, 1988).  Furthermore, young children have been found to look longer at objects for which they know the name, compared to objects of an unknown name (Schafer & Plukett, 1998). In other words, in absentia of a label, infants may be more or less likely to fixate on an unfamiliar object. To account for inherent preferences to the target or distractor image, mispronunciation experiments typically compare the increase in fixations to the target image from a silent baseline to post-labeling or present the same yoked pairs of target and distractor images in in both a correct and mispronounced labelling context. Considering this evidence, we may expect that in older, but not younger, children, the presence of an unfamiliar distractor may lead to greater mispronunciation sensitivity than in the presence of a familiar distractor.

  Furthermore, when presenting infants with a familiar distractor image, some studies control the phonological overlap between the labels for the target and distractor. For example, when examining sensitivity to a mispronunciation of the target word "dog", the vowel mispronunciation "dag" would be paired with a distractor image that shares onset overlap, such as "duck". This ensures that infants can not use the onset of the word to differentiate between the target and distractor images (Fernald, Swingley, & Pinto, 2001). Instead, infants must pay attention to the mispronounced phoneme in order to successfully detect the change. The influence of distractor overlap also depends on the position of the mispronunciation in the word, which can be at word onset, medial, or final positions. Models of spoken word processing place more or less importance on the position of a phoneme in a word.  The COHORT model (Marslen-Wilson & Zwitserlood, 1989) describes lexical access in one direction, with the importance of each phoneme decreasing as its position comes later in the word.  In contrast, the TRACE model (McClelland & Elman, 1986) describes lexical access as constantly updating and reevaluating the incoming speech input in the search for the correct lexical entry, and therefore can recover from word onset and to a lesser extent medial mispronunciations.

  TRACE has also been used to model infants' sensitivity to mispronunciation location (Mayor & Plunkett, 2014), finding that as lexicon size increases, so does sensitivity to onset mispronunciations, whereas medial mispronunciations do not experience similar growth. In early language acquisition, infants typically know more consonant compared to vowel onset words. When tested on their recognition of familiar words, therefore, younger infants would show greater sensitivity to onset mispronunciations, which are frequently consonant mispronunciations. The prevalence of consonant onset words may contribute to the finding that consonants carry more weight in lexical processing (C-bias; see Nazzi, Poltrock, & Von Holzen, 2016 for a recent review). In mispronunciation sensitivity, this would translate to consonant mispronunciations impairing word recognition to a greater degree than vowel mispronunciations. Yet, the handful of studies directly comparing sensitivity to consonant and vowel mispronunciations mostly find symmetry as opposed to an asymmetry between consonants and vowels. English-learning 12-, 15-, 18-, and 24-month-olds (Mani & Plunkett, 2007; 2010 keps and tups) and Danish-learning 20-month-olds (Hojen et al., unpublished) demonstrate similar sensitivity to consonant and vowel mispronunciations. One study did find weak evidence for greater sensitivity to consonant compared to vowel mispronunciations (Swingley, 2016). The English-learning infants tested by Swingley were older than previous studies (mean age 28 months). In word learning, the C-bias has been found to develop later in English learning infants (Floccia, Nazzi, Delle Luche, Poltrock, & Goslin, 2014; Nazzi, Floccia, Moquet, & Butler, 2009). In the current meta-analysis, we attempt to synthesize studies examining sensitivity to consonant and vowel mispronunciations across different ages to determine whether infants generally exhibit more sensitivity to consonant compared to vowel mispronunciations in familiar word recognition as predicted by a learned account of C-bias emergence (Floccia et al., 2014; Keidel et al., 2007; Nazzi et al., 2016). We further examine the impact of language family on mispronunciation sensitivity to consonants and vowels, as C-bias emergence has been found to have a different developmental trajectory for Romance (French, Italian) compared to Germanic (British English, Danish) languages (Nazzi et al., 2016).

[KATIE] Christina had noted something to herself for this paragraph: Subset by language?

  Finally, mispronunciation sensitivity in infants has been examined in many different languages, such as English, Spanish, French, Dutch, German, Catalan, Danish, and Mandarin Chinese (see Summary_Table). Infants learning different languages have different ages of acquisition for words in their early lexicon, leaving direct comparisons between languages within the same study difficult and as a result rare. Yet, studies testing infants from different language backgrounds on similar sets of stimuli find similar sensitivity to mispronunciations (Ramon-Casas et al., 2009; Ramon-Casas & Bosch, 2010). Although we do not explicitly compare overall mispronunciation sensitivity by language (although see previous paragraph for rationale to test by language family), we assess evidence of mispronunciation sensitivity from many different languages using a meta-analytic approach.

Taken together, the studies we have reviewed begin to paint a picture of the development of mispronunciation sensitivity. Each study contributes one separate brushstroke and it is only by examining all of them together that we can achieve a better understanding. In our analysis, we examine the factors modulating the development of mispronunciation sensitivity, which are both of theoretical and practical importance. Meta-analyses can not only help us summarize the current state of research, but can also help us evaluate theories to drive future research and make hands-on recommendations for experiment planning.

@@

[KATIE] THIS TABLE IS DEFINITELY NOT FINISHED!
[CHRISTINA suggestions: N features should be a range and exclude 0; we could abbreviate Comperehension/Production to Comp./Prod., etcetc]
[KATIE] I'll think about how to implement that! Might end up having to adjust the table by hand, there is a lot of variation between studies.

@@

@@

@@

#kable(es_info)
#table(dat$es_method, dat$short_cite)
# only missing from:
# Bailey & Plunkett (2002) <- crazy old data
# Renner (2017) <- just finished phd
#table(db_ET_MP$es_method)

#[KATIE] Can you also rename the factors here (like t_one)?
#[CHRISTINA] Mpt sire what you man, like in the table? You rename things later on, so why not.
#[KATIE] Actually, do we really need this table? When everything is summarized in the text, is that good enough?

corr_info <- dat %>%
  group_by(imputed_corr) %>%
  summarize(n_unique = n_distinct(short_cite), count = n())

@@

We calculated Hedges' *g* using the raw means and standard deviations reported in the paper (*n* = `r with(dat, n_distinct(short_cite[es_method == "group_means_one" | es_method == "group_means_two"]))`) or using reported t-values (*n* = `r with(dat, n_distinct(short_cite[es_method == "t_one" | es_method == "t_two"]))`). Raw means and standard deviations were extracted from figures for `r with(dat, n_distinct(short_cite[ x_from_graph == "yes"]))` papers. In a within-participation design, when two means are compared (i.e. looking during pre- and post-naming) it is necessary to obtain correlations between the two measurements at the participant level to calculate effect sizes and effect size variance based on t-values. Upon request we were provided with correlation values for one paper (Altvater-Mackensen, 2010); we were able to compute correlations using means, standard deviations, and t-values for *n* = `r with(corr_info, n_unique[imputed_corr == "no"]) - 1` (following Csibra, et al. 2016, Appendix B; see also Rabagliati, Ferguson, & Lew-Williams, 2018). Correlations were imputed for the remaining papers (see Black & Bergmann, 2017, for the same procedure). We could compute a total of `r sum(dat$is_mp == 0)` effect sizes for correct pronunciations and `r sum(dat$is_mp == 1)` for mispronunciations.

@@

[CHRISTINA: Do you think we have to revise this section? I think it's the same as in the proceedings paper.]
[KATIE: Are you concerned about the Publication Bias section in particular, or the Methods as a whole? In general, some of the Methods was written before the CogSci paper and in other places to flesh things out I rewrote what we had. Its definitely giving the same information and sometimes the wording is close, because there's not too many different ways to explain what a funnel plot is :)]

@@

[CHRISTINA: Let's both reread the full paper once it is ready and check that this is properly motivated and whether we do need to list them all. For now I think the last sentence is fine, but I would tend to prefer a reminder for the forgetful reader.]
[KATIE: that's reasonable! We had just listed everything 7 paragraphs before, which doesn't seem like a lot of "space".]

@@

[CHRISTINA: If we want to interpret here, how about the next bit.]
[KATIE: YES! This is an excellent point!!!]

The stronger publication bias for correct pronunciation might reflect the status of this condiction as a control. If infants were not looking to the target picture after hearing the correct label, the overall experiment design is called into questions. However, due to the small effect and sample sizes (which we will discuss in the following sections in more detail) one would expect the regular occurrence of null results even though as a population infants would reliably show the expected object identification effect.

@@

[CHRISTINA: CAn you add the stats for the non-sig results?]
[KATIE: Are there stats that can be computed on the non-sig results? Or do you just want an n for significant and non-significant studies?]

Taken together, the results suggest a tendency in the literature towards publication bias. As a result, our meta-analysis may systematically overestimate effect sizes and we therefore interpret all estimates with caution. Yet, the p-curve analysis suggests that overall, the literature contains evidential value, reflecting a "real" effect. We therefore continue our meta-analysis.

@@

We first calculated the meta-analytic effect for object identification, i.e. looks to the target image in response to correctly pronounced words. The variance-weighted meta-analytic effect size Hedges' *g* was `r r2(sum_eff$estimate)` (SE = `r r2(sum_eff$se)`) which was significantly different from zero (95% CI [`r r2(sum_eff$ci.lb)`, `r r2(sum_eff$ci.ub)`], *p* `r psig(sum_eff$pval)`). This is a rather large effect size (according to the criteria set by Cohen, 1988; see also Bergmann, et al., 2018; for comparative meta-analytic effect sizes in language acquisition research). That the effect size is significantly above zero suggests that when presented with the correctly pronounced label, infants fixated the corresponding object. Our analysis of funnel plot asymmetry, however, found evidence for publication bias, which might lead to an overestimated effect sizes as smaller, non-significant results might not be published. Although the effect size Hedges' *g* may be overestimated for object identification in response to correctly pronounced words, the p-curve results and a CI lower bound of `r r2(sum_eff$ci.lb)` suggests that this result is robust even when correcting for publication bias. In other words, we are confident that the true population mean lies above zero for object recognition of correctly pronounced words.

[CHRISTINA: Can you explain what the CI lower bound means here? I don't follow.]
[KATIE: What do you think about this? The CI lower bound stuff here actually comes from something you wrote, so tell me whether its correct.]

@@

[CHRISTINA] CAN YOU ADD ESTIMATES AND THEIR CIS?? Ideally everywhere where you report a p-value
[KATIE: Do you know how to calculate Estimates and CIs for the Test of Moderators? Or do you mean reporting the estimates and CIs even when the moderator test is not significant?]

@@

[KATIE] I DON'T KNOW HOW TO INTERPRET THESE RESULTS... THE FIXED EFFECTS MODEL ISN'T SIGNIFICANT FOR ANY OF THESE. IS THAT MEANINGFUL?
[CHRISTINA] SO WE DON'T WANT TO INTERPRET THE FIXED EFFECTS MODEL AT ALL, IT IS NOT SUITABLE BECAUSE THERE IS VARIANCE BETWEEN EVERY RECORD (LANGUAGE ETC).
I WOULD INTERPRET THE OVERALL CORRELATION AND THE CI, NOT THE P-VALUE (IN GENERAL). I ALSO WONDER WHETHER WE SHOULD MOVE THE SUBSET ANALYSES TO THE SUPPLEMENTARY MATERIALS AND JUST SAY OVERALL WE SEE NO RELATIONSHIPS AND CORRELATION COEFFICIENTS CONSISTENYL BELOW .1
WE THEREFORE MUST CONCLUDE THAT WITHIN NARROW AGE GROUPS VOCABULARY DOES NOT INFLUENCE ANYTHING WE LOOK AT. WE CANNOT DO THIS ANALYSIS FPOR MP SENSITIVITY BECAUSE WE DON'T HAVE THE NECESSARY RAW DATA.
[KATIE: Ah, so because for each paper the correlation and CI values straddle 0, this indicates that there really isn't much evidence for a relationship? I think it could make sense to add this to supplementary materials. Over the summer, I had also played around with looking at how collection of vocabulary data has dropped off over the years, even though more mispronunciation studies have been published. That might be something interesting to add. If we truly think that this is what is driving the development of mispronunciation sensitivity, then why are people not collecting this data?]
(BUT I WONDER WHETHER WECOULD ENCODE THE REPORTED INTERACTION TERMS AND THE CORRELATION AND THEN DO SOMETHING WITH THAT?)
[KATIE: I'm not really sure what you mean by this :(]

@@

[KATIE: I prefer this second option, first looking at the moderators in general and then looking at whether there is this systematic difference with age. The latter is exploratory, so I feel like this information should not preceed our planned analyses.]

### Number of features changed

@@

@@

[KATIE: I think so. I've just removed that part]

@@

\newpage

# References
```{r create_r-references}
#r_refs(file = "r-MISP_MA_BIB.bib")
```

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id = "refs"></div>
\endgroup
